%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%2345678901234567890123456789012345678901234567890123456789012345678901234567890
%        1         2         3         4         5         6         7         8
% THESIS CHAPTER

\chapter{Introduction}
\label{chap:first}
% little histotic intro, definition of robot use in industy up to now
The first robotics systems employed in factory settings made their appearance in the sixties. A robot was able to perform repetitive tasks quickly and precisely and could work in dangerous environments. They were, however, dangerous themselves and for this, even today most robots on the factory floor are kept strictly separated from the human workers through the use of safety cages that are used as a \textit{kill-switch}. Meaning that if the work cell is not closed and free, the robot will not resume any operations.\\
% describe new industrial revolution and HRC with specific challenges
\noindent As stated in \cite{industry_4p0_review}, with the recent advent of Industry "4.0" we entered a new era for robotics. Following the progress in computational power of modern systems, robots became able to perform much more complex tasks, thanks also to the improved ambient perception and analysis capabilities. The focus shifted from the enclosed workspace to having robotic and human agents "cooperating" for a common objective, with the robot taking up the burden of the human worker, especially for physically demanding tasks.\\
\noindent This novel area of robotics presents some specific challenges:
\begin{itemize}
	\item \textbf{Robot vision}: The robot needs to perceive the environment, possibly recognizing elements from the work cell.
	% to talk about the proximity sensor and vision system
	\item \textbf{Human-Robot cooperation}: To achieve a common goal, in a efficient way the robotic and human agent may have to move at the same time while keeping the human safe. 
	% talking about the control and Thesis objective
	\item \textbf{Human-Robot contact}: In the work cell contact with the robot is expected and the robot must be able to differentiate between safe and non-safe contact.
	% to metion the tactile sensor
\end{itemize}
\noindent Given the general complexity of the task at hand, most application are focused on low-payload manipulator, to bridge the gap to high-payload application the \textbf{SestoSenso Project} was born. This project proposes a framework for Human-Robot Collaboration in which coexistence of a human and a robot in the same environment is given, and also controlled physical contact is not only possible but expected.\\
\noindent The robot is expected to be able to perceive the environment of the workstation and be able to follow the assigned task without endangering the human or obstructing the workflow. The vision system of the proposed architecture is based on arrays of \textit{Time of Flight} or \textit{ToF} sensors, allowing the robot to sense the environment and create a 3D representation suitable to maneuver the robot safely. In addition, several robot links are covered with a tactile skin, made of pressure sensor, enabling the system to detect and interpret physical contact with the environment or with the human collaborator. The sensing apparatus was also developed in the MACLAB(Mechatronics and Automatic Control Laboratory) and is described in \cite{proxySkin_paper}.

\noindent The SestoSenso robotic setup presents a series of novelty approaches that differentiate it from conventional human-robot collaboration frameworks:
\begin{itemize}
	\item \textbf{Kinematic structure}
	\item \textbf{Payload capabilities}
	\item \textbf{Point cloud based sensing}
\end{itemize}
\noindent The robotic agent is composed of two stages, for a total of 12 degrees of freedom, created by combining two manipulators: a high-payload industrial arm from KUKA as the first stage, and a lightweight, highly compliant arm from Universal Robots as the second stage. This configuration was chosen to leverage the redundancy of the kinematic chain to follow multiple objective simultaneously. The KUKA is able to move payload up from $150$kg, and is generally considered a \textit{high-payload} application robot. Lastly the discrete point cloud sensing allows for a reactive based control, increasing the responsiveness to changes in the work environment.  


\section{Research problem and objective}
\noindent My thesis was developed along side this project, and aims to build and test a unified control architecture for the two robots. During the project development, some technical complication were encountered in the control of the two robots.\\
\noindent Due to the commercial nature of the two robotic systems, the control interfaces were different and required different types of communication protocol for the two stages of the robot. Moreover the control algorithms were blocked behind the proprietary software of the manufacturer, allowing the team to rely only on kinematic control. This resulted in frequent \textit{safety stops} due to the reaction forces generated in the Kuka joints whenever the two robots moved simultaneously. The research team decided than to move only one stage at a time, giving up the redundancy of the system.
Since my thesis was developed using a kinematic simulation, I could test the robot moving the complete 12 DoF chain. My main focus was to explore how the robot used the redundancy in the chain, to achive motion in a obstructed environment.\\
\noindent All the activities were carried out at MACLAB, the Mechatronics and Automatic Control Laboratory at Università degli Studi di Genova.

\section{Thesis structure}
After the brief introduction in Chap.\ref{chap:first} of the objective of this thesis, in Chap. \ref{chap:second} I will provide the state of the art for: technologies used for ambient sensing, their strength and weaknesses related to this specific application. 
\noindent Approaches of \textit{obstacle avoidance} for manipulators, and redundancy control. Finally a general discussion on various types of High-Dof structures. 
The Chap. \ref{chap:third} will be a discussion on the mathematical foundation of algorithms and methods I used in my work.
In Chap.\ref{chap:fourth} instead the focus will be on the architecture implementation, describing the functionalities I included and how the system works.
Lastly \ref{chap:fifth} will be the presentation of the simulation environment and the experiments I carried out. The conclusion are in Chap.\ref{chap:conclusions}.
 